Figures

### 2019-05-17 figures/08_exploratory_dotplot.Rmd
show n dep dotplot

```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE}
dt     <- readRDS("../data/dt.rds")
dt_sub <- dplyr::select(dt, tp, tn, lake_area_ha:wheat, -other.non.ag, 
                        -mixed.crop) %>%
  dplyr::filter(complete.cases(.)) %>%
  mutate_all(as.numeric) %>%
  data.frame(stringsAsFactors = FALSE)

dt_tp <- dt_sub %>%
  corrr::correlate() %>%
  corrr::shave() %>%
  janitor::remove_empty(c("rows", "cols")) %>%
  mutate_if(is.numeric, round, 2) %>%
  arrange(desc(abs(tp))) %>%
  data.frame() %>%
  dplyr::select(rowname, tp, tn)

@@

>>>>

```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE}
dt     <- readRDS("../data/dt.rds")
dt_sub <- dt %>% 
  dplyr::select(tp, tn, lake_area_ha:wheat, 
                matches("cultivated_crops")) %>%
  dplyr::select(-row_crop_pct, -ag_pct, -pasture_pct) %>% # rm nlcd
  dplyr::select(-mixed.crop, -matches("other"), -forage, 
                -hu12_ppt_std, -water, -developed, -forest) %>% # rm junk
  dplyr::filter(complete.cases(.)) %>%
  mutate_all(as.numeric) %>%
  data.frame(stringsAsFactors = FALSE)

dt_tp <- dt_sub %>%
  corrr::correlate() %>%
  # corrr::shave() %>%
  janitor::remove_empty(c("rows", "cols")) %>%
  mutate_if(is.numeric, round, 2) %>%
  arrange(desc(abs(tp))) %>%
  data.frame() %>%
  dplyr::select(rowname, tp, tn)

@@

```{r n-dep_dotplot}

slice_cormat <- function(var_name, dt_sub){
  # var_name <- "nitrogen_atmospheric_deposition"

  dt_corr <- dt_sub %>%
    corrr::correlate() %>%
    # corrr::shave() %>%
    janitor::remove_empty(c("rows", "cols")) %>%
    mutate_if(is.numeric, round, 2) %>%
    arrange(desc(abs(!!rlang::sym(var_name)))) %>%
    data.frame() %>%
    dplyr::select(rowname, var_name)

  dt_corr_rows <- dt_corr$rowname
  dt_corr <- dt_corr %>%
    dplyr::select(-rowname) %>%
    mutate_all(abs)
  row.names(dt_corr) <- dt_corr_rows

  dt_corr
}

test <- slice_cormat("nitrogen_atmospheric_deposition", dt_sub)

ggplot(data = prep_dotplot(test, "nitrogen_atmospheric_deposition")) +
    geom_point(aes(x = nitrogen_atmospheric_deposition, y = var)) +
    plot_opts
